Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-20 vesicle_code/docs/adhesion/adhesion.tex
yny adhesion 1st round on july 20

The adhesion potential for a vesicle membrane has been modeled by a
L.-J.~type potential
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = \mathcal{H} \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion
length scale, and $z$ is the distance between a patch on the vesicle
membrane and a point on the other object, which could be another vesicle
membrane or a flat solid wall.  The characteristics of the
L.-J.~potential are summarized in Figure~\ref{fig:adhesionModel}(a): The
adhesive force is zero at the equilibrium distance $z=\delta$.  For
large distances ($z > \delta$) the adhesive potential is attractive
while for small distances ($z < \delta$) the potential is repulsive to
prevent physical contact. The long-range attraction component should
decay sufficiently fast to mimic the finite-range attraction between
RBCs. However, here to simplify the formulation we do not introduce such
a truncation in the attraction.

@@

Two main observations that can be drawn from the results in
Figure~\ref{fig:extensionalNonsymmetric} are: (1) The membrane tension is
highly non-uniform on the vesicles, leading to a significant Marangoni
stress along the membrane as in the case of a surfactant-laden drop at
the center of an extensional flow. Thus it is reasonable to expect that
the flow around the vesicles is significantly altered.  (2) In an
extensional flow, vesicles are prone to move away from the stagnation
point.  A small initial vertical displacement $\Delta y$ in one  of the
vesicles causes both vesicles to not only rotate but also move away from
the center. Once vesicles move off the horizontal axis, their
hydrodynamics is dominated by the diverging flow as they move farther
away.  Thus in the microfluidic experiment it is often more desirable to
trap the vesicle around the center of an extensional
flow~\cite{Spjut2010_MSThesis_Chapter3}. With an active control
algorithm to place the stagnation point at a desirable location by
adjusting the flow with a feedback
loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle
can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as particle
image velocimetry of flow inside and around the particle.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a planar shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the planar shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another in a
head-on collision.  In the absence of adhesion, once the vesicles are
sufficiently close, they are deflected to opposite sides of the $y$
axis, pass one another, and then separate. This head-on collision
process of two vesicles or capsules in a planar shear flow is found to
be similar between
two-~\cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP, RahimianVeerapaneniBiros2010_JCP} and
three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,
OmoriIshikawaImaiYamaguchi2013_JBiomechics,
RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
adhesion, the vesicles can form a doublet for certain values of the
separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
it undergoes a periodic motion with a period that depends on the same
parameters.

Figures~\ref{fig:doublet090-weakAdhesion}
and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
that have formed a doublet and the color coding is the tension along the
vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
rate $\dot\gamma = 0.5$, separation distance $\delta = 0.4$, and Hamaker
constant $\mathcal{H} = 0.7$ (Figure~\ref{fig:doublet090-weakAdhesion})
and $\mathcal{H} = 2.1$ (Figure~\ref{fig:doublet090-strongAdhesion}).
Similar to the quiescent example, the membrane tension is negative in
the contact region indicating that the membrane is being compressed when
the adhesive force is strongest.  The two values for the Hamaker
constant are chosen since the period of the dynamics of the doublets are
both $t^* \approx 42$.  For both the Hamaker constants, the vesicles in
the doublet move in tandem with a tank-reading motion that is much
slower than the tank-treading motion that occurs in the absence of
adhesion.  However, the dynamics of a single period for theses two
Hamaker constants differ significantly.  For the weaker adhesive force,
the individual vesicles undergo a sliding motion as they pass one
another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, at larger
Hamaker constants, once the contact region is formed, the doublet
maintains the same structure and undergoes a tumbling dynamic similar to
a Jeffery orbit.

@@

To further understand the formation of the doublet, we compute the
distance between two vesicles with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.5$, and shear rate $\dot\gamma = 0.5$.
Figure~\ref{fig:sflow_distance}(a) shows this minimum distance as a
function of time for varying Hamaker constants.  For Hamaker constants
less than a critical value, $\mathcal{H}_c$, the adhesive force is not
strong enough to form a doublet, and the distance between the vesicles
grows with time (red curves).  However, when $\mathcal{H} >
\mathcal{H}_c$, the adhesive force is sufficiently strong to bind the
vesicles into a doublet, and then the doublet undergoes a periodic
motion (blue curves).  In Figure~\ref{fig:sflow_distance}(b), we plot
the time required for the doublet to make a complete revolution for
three different shear rates and two different separation distances.
Initially, as the shear rate increases, the period decreases.  However,
the transition from the weakly adhesive doublet
(Figure~\ref{fig:doublet090-weakAdhesion}) to the stronger adhesive
doublet (Figure~\ref{fig:doublet090-strongAdhesion}) results in an
increase in the period.  Once the Hamaker constant is sufficiently
strong that the contact region remains fixed throughout the dynamics,
the period of the doublet again decreases as the shear rate increases.

Especially at the large Hamaker constants, the dynamics of the doublet
resemble those of a Jeffery orbit.  An ellipse with aspect ratio
$\lambda$ undergoes a periodic tumbling motion with
period~\cite{jef1922}
\begin{align}
  p = \frac{2\pi}{\dot\gamma}\left(\lambda + \lambda^{-1} \right).
  \label{eqn:JefferyPeriod}
\end{align}
Instead of measuring the aspect ratio of a doublet in a flow with shear
rate $\dot\gamma$, we use the computed period to define an effective
aspect ratio $\lambda_{\mathrm{eff}}$ that
satisfies~\eqref{eqn:JefferyPeriod}.  Therefore, the effective aspect
ratio is the aspect ratio of an ellipse in a shear flow that is
undergoing a Jeffery orbit with period $p$.  For the Hamaker constants
$\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the shear rates, periods,
and effective aspect ratio are summarized in
Table~\ref{tbl:aspectRatio}.  The effective aspect ratio of the doublet
depends on both the Hamaker constant and the shear rate, and this
indicates that the doublet's dynamics differ from those of a rigid body
undergoing a Jeffery orbit.

\begin{table}[htp]
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 1.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
%  0.50 & 38.06 & 2.92 \\
%  0.75 & 24.81 & 2.85 \\
%  1.00 & 19.47 & 3.00 
  0.50 & 36.34 & 2.49 \\
  0.75 & 25.86 & 2.72 \\
  1.00 & 20.73 & 2.96 
\end{tabular}
\end{minipage}
%\hfill
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 3.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 28.46 & 1.66 \\
  0.75 & 22.01 & 2.17 \\
  1.00 & 17.91 & 2.44 
\end{tabular}
\end{minipage}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.4$, and 
Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$.  The
effective aspect ratios depend on both the Hamaker constant and the
shear rate, indicating that for the reported Hamaker constants, the
dynamics of the doublet differ from that of a Jeffery orbit.}
\end{table}

@@

\begin{figure}
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
  \end{tabular}
  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
  separation distance $\delta = 0.4$.  The different lines correspond to
  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
  the separation distance is $\delta = 0.4$.  The different lines
  correspond to different shear rates and separation distances.}
\end{figure}

@@

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\dot\gamma \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.  In
Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet with Hamaker
constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
shear rate $\dot\gamma = 0.5$.  To validate our simulations, we
superimpose (black marks) the intrinsic viscosity calculated by
Ghigliotti {\em et al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The
presence of the doublet slightly increases the intrinsic viscosity at
all the reduced areas.  We also compute the intrinsic viscosity of a
doublet with $\Delta A = 0.9$, $\dot\gamma = 0.5$, and $\mathcal{H} =
2.1$.  Again, this doublet has a similar period to the case $\mathcal{H}
= 0.7$. At this larger Hamaker constant, the effective viscosity
increases slightly from $1.97$ to $2.06$.  To further characterize the
effect of adhesion, in Figure~\ref{fig:shearIntrinsicViscosity}(b) we
decompose the intrinsic viscosity into the contributions from the
bending and tension (black), and the contribution from the adhesion
(green).  We also superimpose the intrinsic viscosity of a single
tank-treading vesicle (blue) to demonstrate that the bending and tension
of the doublet behave similarly, but not identically, to a dilute
suspensions of non-adhering tank-treading vesicles.  We see that the
effect of the adhesion on the intrinsic viscosity is largest for
vesicles with small reduced areas.  We also decompose the intrinsic
viscosity contributions of the doublet with $\mathcal{H} = 2.1$ and
$\Delta A = 0.9$.  When compared with the smaller Hamaker constant, the
intrinsic viscosity contribution due to bending and tension is reduced
from $1.85$ to $1.71$, and the contribution due to adhesion is increased
from $0.12$ to $0.36$.  Therefore, as the Hamaker constant increases,
the increase in the intrinsic viscosity is due to the adhesive force
rather than the bending and tension.

\begin{figure}[]
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
  \end{tabular}
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
  = 0.7$, and the separation distance $\delta = 0.4$.  The black
  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
  decomposition of the intrinsic viscosity into the contributions for
  the bending and tension (black) of the vesicles, and the contribution
  from the vesicle adhesion (green).  Also included is the intrinsic
  viscosity of a single tank-treading vesicle (blue).}
\end{figure}

>>>>

The adhesion potential for a vesicle membrane has been modeled by a
L.-J.~type potential
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = \mathcal{H} \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion
length scale, and $z$ is the distance between a patch on the vesicle
membrane and a point on the other object, which could be another vesicle
membrane or a flat solid wall.  The characteristics of the
L.-J.~potential are summarized in Figure~\ref{fig:adhesionModel}(a): The
adhesive force is zero at the equilibrium distance $z=\delta$.  For
large distances ($z > \delta$) the adhesive potential is attractive
while for small distances ($z < \delta$) the potential is repulsive to
prevent physical contact. The long-range attraction component should
decay sufficiently fast to mimic the finite-range attraction between
RBCs. In this work we are mainly interested in effects of adhesive 
interactions between two vesicles drawn together by the surrounding linear flow.
Therefore we  do not introduce any truncation in the long-range attraction.

@@

Here we provide two main observations drawn from the results in
Figure~\ref{fig:extensionalNonsymmetric}: (1) The membrane tension is
highly non-uniform on the vesicles, leading to a significant Marangoni
stress along the membrane as in the case of a surfactant-laden drop at
the center of an extensional flow. Thus it is reasonable to expect that
the flow around the vesicles is significantly altered.  (2) In an
extensional flow, vesicles are prone to move away from the stagnation
point.  A small initial vertical displacement $\Delta y$ in one  of the
vesicles causes both vesicles to not only rotate but also move away from
the center. Once vesicles move off the horizontal axis, their
hydrodynamics is dominated by the diverging flow as they move farther
away.  Thus in the microfluidic experiment it is often more desirable to
trap the vesicle around the center of an extensional
flow~\cite{Spjut2010_MSThesis_Chapter3}. With an active control
algorithm to place the stagnation point at a desirable location by
adjusting the flow with a feedback
loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle
can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as particle
image velocimetry of flow inside and around the particle.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a planar shear flow}
\label{sec:sflow} 
We consider two vesicles under a planar shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another in a
head-on collision.  In the absence of adhesion,  
two vesicles deform significantly as they collide head-on, 
deflect to opposite sides of the $y$-axis as they pass one another, and then separate.
This head-on collision
process of two vesicles or capsules in a planar shear flow is found to
be similar between
two-~\cite{Breyiannis-Pozrikidis:2000,RahimianVeerapaneniBiros2010_JCP, RahimianVeerapaneniBiros2010_JCP} and
three-dimensions~\cite{LacMorelBarthes-Biesel2007_JFM,LacBarthes-Biesel2008_PoF,
OmoriIshikawaImaiYamaguchi2013_JBiomechics,
RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
adhesion, the vesicles can form a doublet for certain values of the
separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
it undergoes a periodic motion with a period that depends on the same
parameters.

Figures~\ref{fig:doublet090-weakAdhesion}
and~\ref{fig:doublet090-strongAdhesion} show snapshots of 
two vesicles
that have formed a doublet and the color coding is the tension along the
vesicle.  Each of the vesicles have reduced area $\Delta A = 0.9$, shear
rate $\dot\gamma = 0.5$, separation distance $\delta = 0.4$, and Hamaker
constant $\mathcal{H} = 0.7$ (Figure~\ref{fig:doublet090-weakAdhesion})
and $\mathcal{H} = 2.1$ (Figure~\ref{fig:doublet090-strongAdhesion}).
Similar to the quiescent example, the membrane tension is negative in
the contact region indicating that the membrane is being compressed when
the adhesive force is strongest.  The two values for the Hamaker
constant are chosen since the oscillation period of the vesicle doublet dynamics is
both $t^* \approx 42$.  For both cases the vesicles in
the doublet move in tandem with a tank-reading motion that is much
slower than the tank-treading motion that occurs in the absence of
adhesion.  However, the dynamics of a single period for theses two
Hamaker constants differ significantly.  For $\mathcal{H} = 0.7$
the individual vesicles undergo a sliding motion as they pass one
another (Figure~\ref{fig:doublet090-weakAdhesion}).  However, for $\mathcal{H} = 2.1$, once the contact region is formed, the doublet
maintains the same structure and undergoes a tumbling dynamic similar to
a Jeffery orbit.

@@

To further understand the formation of the doublet, we compute the center-to-center
distance between two vesicles with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.5$, and shear rate $\dot\gamma = 0.5$.
Figure~\ref{fig:sflow_distance}(a) shows this distance as a
function of time for varying Hamaker constants.  For Hamaker constants
less than a critical value, $\mathcal{H}_c$, the adhesive force is not
strong enough to form a doublet, and the distance between the vesicles
grows with time (red curves).  However, when $\mathcal{H} >
\mathcal{H}_c$, the adhesive force is sufficiently strong to bind the
vesicles into a doublet, and then the doublet undergoes a periodic
motion (blue curves).  In Figure~\ref{fig:sflow_distance}(b), we plot
the time required for the doublet to make a complete revolution for
three different shear rates and two different separation distances.
Initially, as the shear rate increases, the period decreases.  However,
the transition from the weakly adhesive doublet
(Figure~\ref{fig:doublet090-weakAdhesion}) to the stronger adhesive
doublet (Figure~\ref{fig:doublet090-strongAdhesion}) results in an
increase in the period.  Once the Hamaker constant is sufficiently
strong that the contact region remains fixed throughout the dynamics,
the period of the doublet again decreases as the shear rate increases.
\begin{figure}
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
  \end{tabular}
  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
  separation distance $\delta = 0.4$.  The different lines correspond to
  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
  the separation distance is $\delta = 0.4$.  The different lines
  correspond to different shear rates and separation distances.}
\end{figure}

Especially at the large Hamaker constants, the dynamics of the doublet
resemble those of a Jeffery orbit.  An ellipse with aspect ratio
$\lambda$ undergoes a periodic tumbling motion with
period~\cite{jef1922}
\begin{align}
  p = \frac{2\pi}{\dot\gamma}\left(\lambda + \lambda^{-1} \right).
  \label{eqn:JefferyPeriod}
\end{align}
Instead of measuring the aspect ratio of a doublet in a flow with shear
rate $\dot\gamma$, we use the computed period to define an effective
aspect ratio $\lambda_{\mathrm{eff}}$ that
satisfies~\eqref{eqn:JefferyPeriod}.  Therefore, the effective aspect
ratio is the aspect ratio of an ellipse in a shear flow that is
undergoing a Jeffery orbit with period $p$.  For the Hamaker constants
$\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$, the shear rates, periods,
and effective aspect ratio are summarized in
Table~\ref{tbl:aspectRatio}, which illustrates that 
the effective aspect ratio of the doublet
depends on both the Hamaker constant and the shear rate.
%
\begin{table}[htp]
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 1.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
%  0.50 & 38.06 & 2.92 \\
%  0.75 & 24.81 & 2.85 \\
%  1.00 & 19.47 & 3.00 
  0.50 & 36.34 & 2.49 \\
  0.75 & 25.86 & 2.72 \\
  1.00 & 20.73 & 2.96 
\end{tabular}
\end{minipage}
%\hfill
\begin{minipage}{0.45\textwidth}
  $\mathcal{H} = 3.5$ \\
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\dot\gamma$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 28.46 & 1.66 \\
  0.75 & 22.01 & 2.17 \\
  1.00 & 17.91 & 2.44 
\end{tabular}
\end{minipage}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
separation distance $\delta = 0.4$, and 
Hamaker constants $\mathcal{H} = 1.5$ and $\mathcal{H} = 3.5$.  The
effective aspect ratios depend on both the Hamaker constant and the
shear rate, indicating that for the reported Hamaker constants, the
dynamics of the doublet differ from that of a Jeffery orbit.}
\end{table}
%
Furthermore the oscillatory dynamics in Figure~\ref{fig:doublet090-weakAdhesion} and Figure~\ref{fig:doublet090-strongAdhesion} 
illustrate that for similar oscillation periods, the actual aspect ratio of the vesicle doublet may be a dynamical variable as well.
This
indicates that the vesicle doublet's oscillatory dynamics in a shear flow is more complicated than the Jeffery orbit a rigid body.

@@

%\begin{figure}
%  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
%  \subfigimg[width=\linewidth]{(a)}{figs/shear_adR4em1Chi5em1_ra090.pdf} &
%  \subfigimg[width=\linewidth]{(b)}{figs/shear_adR4em1Chi5em1_ra090_period.pdf}
%  \end{tabular}
%  \caption{\label{fig:sflow_distance} (a) The distance between a pair of
%  vesicles in a planar shear flow with shear rate $\dot\gamma=0.5$, and
%  separation distance $\delta = 0.4$.  The different lines correspond to
%  a linear spacing of Hamaker constants ranging from $\mathcal{H}=0.1$
%  and $\mathcal{H}=1.0$.  (b) The time required for a doublet to
%  complete a single rotation.  The reduced area is $\Delta A = 0.90$ and
%  the separation distance is $\delta = 0.4$.  The different lines
%  correspond to different shear rates and separation distances.}
%\end{figure}

@@

%
%\begin{figure}[]
%  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
%  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
%  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
%  \end{tabular}
%%  \centering
%%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
%%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
%  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
%  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
%  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
%  = 0.7$, and the separation distance $\delta = 0.4$.  The black
%  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
%  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
%  decomposition of the intrinsic viscosity into the contributions for
%  the bending and tension (black) of the vesicles, and the contribution
%  from the vesicle adhesion (green).  Also included is the intrinsic
%  viscosity of a single tank-treading vesicle (blue).}
%\end{figure}
Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\dot\gamma \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.

\begin{figure}[h]
  \begin{tabular}{@{}p{0.45\linewidth}@{\quad}p{0.45\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/doublet_decomp.pdf}
  \end{tabular}
%  \centering
%  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
%  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} (a) The intrinsic
  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
  shear rate $\dot\gamma = 0.5$, the Hamaker constant $\mathcal{H}
  = 0.7$, and the separation distance $\delta = 0.4$.  The black
  marks denote intrinsic viscosity values computed by Ghigliotti {\em et
  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  (b) The
  decomposition of the intrinsic viscosity into the contributions for
  the bending and tension (black) of the vesicles, and the contribution
  from the vesicle adhesion (green).  Also included is the intrinsic
  viscosity of a single tank-treading vesicle (blue).}
\end{figure}
In Figure~\ref{fig:shearIntrinsicViscosity}(a), we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet with Hamaker
constant $\mathcal{H} = 0.7$, separation distance $\delta = 0.4$, and
shear rate $\dot\gamma = 0.5$.  To validate our simulations, we
superimpose (black marks) the intrinsic viscosity calculated by
Ghigliotti {\em et al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The
presence of the doublet slightly increases the intrinsic viscosity at
all the reduced areas.  We also compute the intrinsic viscosity of a
doublet with $\Delta A = 0.9$, $\dot\gamma = 0.5$, and $\mathcal{H} =
2.1$.  Again, this doublet has a similar period to the case $\mathcal{H}
= 0.7$. At this larger Hamaker constant, the effective viscosity
increases slightly from $1.97$ to $2.06$.  To further characterize the
effect of adhesion, in Figure~\ref{fig:shearIntrinsicViscosity}(b) we
decompose the intrinsic viscosity into the contributions from the
bending and tension (black), and the contribution from the adhesion
(green).  We also superimpose the intrinsic viscosity of a single
tank-treading vesicle (blue) to demonstrate that the bending and tension
of the doublet behave similarly, but not identically, to a dilute
suspensions of non-adhering tank-treading vesicles.  We see that the
effect of the adhesion on the intrinsic viscosity is largest for
vesicles with small reduced areas.  We also decompose the intrinsic
viscosity contributions of the doublet with $\mathcal{H} = 2.1$ and
$\Delta A = 0.9$.  When compared with the smaller Hamaker constant, the
intrinsic viscosity contribution due to bending and tension is reduced
from $1.85$ to $1.71$, and the contribution due to adhesion is increased
from $0.12$ to $0.36$.  Therefore, as the Hamaker constant increases,
the increase in the intrinsic viscosity is due to the adhesive force
rather than the bending and tension.
